Intelligent Building Energy Management System

### 2021-05-04 parts/10-introduction.tex
Updated report

\section{Project Description}
The Internet of Things is a large network of embedded devices
\replace{like}{, such as} sensors,
wearables, and appliances capable of receiving control commands and reporting
data over the Internet. Many industries take advantage of this infrastructure to
improve process flow and efficiency. One of these industries is the commercial
and industrial sector which often employ building automation or management
systems to help better manage processes or devices in a building like air
conditioning systems, lights or industrial machines. Technological advancements
have allowed devices to become connected to a building network through
communication protocols like WiFi, Ethernet, Modbus, or BACnet which enables
them to be more easily controlled from a central system.

@@

During a research project led by Miah \textit{et al.,} the DC motor interface was successfully
implemented into the BEMOSS platform which required adding a great deal of
\add{source} code
to the platform to fully implement the device as BEMOSS does not support adding
new devices currently. The research also consisted of adding a new
\add{features, such as } logo to the
platform for the motor. A possible improvement our platform will make is helping
developers on the project to add new devices more easily.

One of the improvements our project makes over the previous is the use of UDP
\add{(user datagram protocol)} multicasting which does not require any superuser privileges to locate an
embedded computer (Beaglebone Blue\add{, for example}). This implementation is also more convenient
because it does not require installing any packages as multicasting is natively
supported by most embedded Linux systems. If in the future, multiple embedded
computers are needed to be discovered, the multicasting system works elegantly
as each device can simply listen on a provided multicast group which consists of
an IP address and port number.

@@

One such platform is the BEMOSS from the Virginia Polytechnic Institute and State
University Advanced Research Institute. BEMOSS features include being
open-source, allowing for multiple communication technologies, and supporting
many common IoT devices. This system allows for monitoring and controlling a
variety of devices securely\todo[inline]{Need citation here}.

Another open-source platform is rEMpy or residential Energy Management in
Python. The main focus of this platform developed by a team of researchers at
Universit\`{a} Politecnica delle Marche in Ancona, Italy was to simulate the
energy flow of a residential home. With the data collected from simulations, it
was possible for them to use forecasting and prediction algorithms to predict
various quantities \replace{like}{, such as} energy usage and power consumption over a given time period. Their energy management system consists of a well-defined structure with components like a user interface, database, and optimal scheduler that communicates with modules like a prediction and thermal model. In terms of software technologies, it uses the Django web framework which provides a lot of built-in functionality for web development like a user-authentication system and object-relational mapping. Adapting the project to this framework could be a great way to help improve security and optimize database queries~\cite{fagiani2017}.

@@

In~\cite{8246800}, \remove{the }authors describe similar functional requirements to our
own BEMS Core. They periodically gather power consumption and device status data
and send that data to a database. We are doing exactly what they describe using
the Apache Cassandra database. The authors also use an "analytics [sic] engine
to process [the data] and generate reports, graphs, and charts." Our system only
generates a power consumption plot for a given day, but we are still meeting
this same requirement - just on a smaller scale. The communication with devices
and power consumption reports are to be accessible through a web-based
application that is easy to use. Again, our implementation is simple and very
intuitive for the end-user. Finally, these authors mention a user-login feature.
They explain that their system would include multiple levels of accessibility
based on the user privileges. Although our system does not currently have a
user-login feature, it simply uses a router to access devices that are also
connected to the router. Since this is a closed system, users need only protect
their router with a secure password.

A control scheme in~\cite{Barchi2018} is presented to manage a photovoltaic
array and battery energy storage system. Tests were conducted in a shopping mall
with an electronic load to emulate the power consumption of the building.
Potentially, a similar technique could be used to model the energy demand of a
house in Simulink or Simscape model. Through their scheme, an intelligent BEMS
is used to collect measurable data \replace{like}{, such as} power, voltage, and current and stored for offline analysis later. Their platform collects data every five minutes compared to the 20 second polling rate currently configured in our platform. A control algorithm was presented proving that grid energy is consumed more heavily during periods of low power demand rather than PV power.

@@

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
This report is organised into 5 chapters.  Chapter \ref{ch: Chapter1} discusses
what this project hopes to accomplish and what similar projects have completed.
Chapter \ref{ch: Chapter2} explains the architecture. Chapter \ref{ch: Chapter3}
provides a brief explanation of the control algorithms and architectures used.
Chapter \ref{ch: Chapter4} contains the results from \replace{our simulations}{a
few experiments}. Chapter \ref{ch: Chapter5} concludes the \replace{paper}{report} and provides insight into future directions.

>>>>

\section{Project Description}
The Internet of Things is a large network of embedded devices such as sensors, wearables, and appliances capable of receiving control commands and reporting
data over the Internet. Many industries take advantage of this infrastructure to
improve process flow and efficiency. One of these industries is the commercial
and industrial sector which often employ building automation or management
systems to help better manage processes or devices in a building like air
conditioning systems, lights or industrial machines. Technological advancements
have allowed devices to become connected to a building network through
communication protocols like WiFi, Ethernet, Modbus, or BACnet which enables
them to be more easily controlled from a central system.

@@

During a research project led by Miah \textit{et al.,} the DC motor interface was successfully
implemented into the BEMOSS platform which required adding a great deal of source code
to the platform to fully implement the device as BEMOSS does not support adding
new devices currently. The research also consisted of adding a new
features such a logo to the
platform for the motor. A possible improvement our platform will make is helping
developers on the project to add new devices more easily.

One of the improvements our project makes over the previous is the use of UDP (user datagram protocol) multicasting which does not require any superuser privileges to locate an
embedded computer (Beaglebone Blue, for example). This implementation is also more convenient
because it does not require installing any packages as multicasting is natively
supported by most embedded Linux systems. If in the future, multiple embedded
computers are needed to be discovered, the multicasting system works elegantly
as each device can simply listen on a provided multicast group which consists of
an IP address and port number.

@@

One such platform is the BEMOSS from the Virginia Polytechnic Institute and State
University Advanced Research Institute. BEMOSS features include being
open-source, allowing for multiple communication technologies, and supporting
many common IoT devices. This system allows for monitoring and controlling a
variety of devices securely~\cite{BEMOSS}.

Another open-source platform is rEMpy or residential Energy Management in
Python. The main focus of this platform developed by a team of researchers at
Universit\`{a} Politecnica delle Marche in Ancona, Italy was to simulate the
energy flow of a residential home. With the data collected from simulations, it
was possible for them to use forecasting and prediction algorithms to predict
various quantities such as energy usage and power consumption over a given time period. Their energy management system consists of a well-defined structure with components like a user interface, database, and optimal scheduler that communicates with modules like a prediction and thermal model. In terms of software technologies, it uses the Django web framework which provides a lot of built-in functionality for web development like a user-authentication system and object-relational mapping. Adapting the project to this framework could be a great way to help improve security and optimize database queries~\cite{fagiani2017}.

@@

In~\cite{8246800}, authors describe similar functional requirements to our
own BEMS Core. They periodically gather power consumption and device status data
and send that data to a database. We are doing exactly what they describe using
the Apache Cassandra database. The authors also use an \say{analytics [sic] engine
to process [the data] and generate reports, graphs, and charts.} Our system only
generates a power consumption plot for a given day, but we are still meeting
this same requirement - just on a smaller scale. The communication with devices
and power consumption reports are to be accessible through a web-based
application that is easy to use. Again, our implementation is simple and very
intuitive for the end-user. Finally, these authors mention a user-login feature.
They explain that their system would include multiple levels of accessibility
based on the user privileges. Although our system does not currently have a
user-login feature, it simply uses a router to access devices that are also
connected to the router. Since this is a closed system, users need only protect
their router with a secure password.

A control scheme in~\cite{Barchi2018} is presented to manage a photovoltaic
array and battery energy storage system. Tests were conducted in a shopping mall
with an electronic load to emulate the power consumption of the building.
Potentially, a similar technique could be used to model the energy demand of a
house in Simulink or Simscape model. Through their scheme, an intelligent BEMS
is used to collect measurable data such as power, voltage, and current and stored for offline analysis later. Their platform collects data every five minutes compared to the 20 second polling rate currently configured in our platform. A control algorithm was presented proving that grid energy is consumed more heavily during periods of low power demand rather than PV power.

@@

%----------------------------------------------------------------------
\section{Report Organization}
%----------------------------------------------------------------------
This report is organised into 5 chapters.  Chapter \ref{ch: Chapter1} discusses
what this project hopes to accomplish and what similar projects have completed.
Chapter \ref{ch: Chapter2} explains the architecture. Chapter \ref{ch: Chapter3}
provides a brief explanation of the control algorithms and architectures used.
Chapter \ref{ch: Chapter4} contains the results from a few experiments. Chapter \ref{ch: Chapter5} concludes the report and provides insight into future directions.

### 2021-05-04 parts/20-iBEMSArchitecture.tex
Updated report

There are 5 general modes of operation in iBEMS as shown in Figure~\ref{fig:operationalModes}. In Mode 0, before iBEMS is even launched, the user must open the Startup Menu, which is a desktop graphical user interface (GUI). This is a simple GUI with only 2 buttons for starting and stopping iBEMS. Upon clicking "Start iBEMS," the login page will load where the user can enter a valid username and password to use iBEMS. Once a valid username and password is entered, the home screen will be shown which displays the weather data being downloaded from the OpenWeatherMap API. This information include temperature in Fahrenheit and Celsius, wind speed in MPH, humidity, and cloud coverage. At this point, a navigation bar is available to view "Active Devices" page and the "Scheduling" page. "Active Devices" corresponds to Mode 3 for controlling devices in real time. The user will also be able to view power plots in this mode as well. Lastly, the "Scheduling" page is Mode 4 for creating schedules for all connected devices.

>>>>

There are 5 general modes of operation in iBEMS as shown in Figure~\ref{fig:operationalModes}. In Mode 0, before iBEMS is even launched, the user must open the Startup Menu, which is a desktop graphical user interface (GUI). This is a simple GUI with only 2 buttons for starting and stopping iBEMS. Upon clicking \say{Start iBEMS}, the login page will load where the user can enter a valid username and password to use iBEMS. Once a valid username and password is entered, the home screen will be shown which displays the weather data being downloaded from the OpenWeatherMap API. This information include temperature in Fahrenheit and Celsius, wind speed in MPH, humidity, and cloud coverage. At this point, a navigation bar is available to view \say{Active Devices} page and the \say{Scheduling} page. \say{Active Devices} corresponds to Mode 3 for controlling devices in real time. The user will also be able to view power plots in this mode as well. Lastly, the \say{Scheduling} page is Mode 4 for creating schedules for all connected devices.

### 2021-05-04 parts/30-Implementation.tex
Updated report

% Talk about Zero MQ
All three agents communicate with each other and the web server using the Zero
MQ asynchronous messaging library\todo{citation here}. Essentially, this library
works as a way to implement inter process communication without a message
broker. In other words, different processes are able to communicate with each
other without any central bus. This is convenient as fewer processes are needed
for the system to function. Lowering the number of overall processes lowers the
RAM and CPU usage of the software. The library is ported to many different
programming languages; however we are using the Python port titled Pyzmq to
implement in our code base.
%
\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{figs/pubSubAgents.pdf}
    \caption{Publish Subscribe Communication using ZeroMQ}
    \label{fig:pubSubAgents}
\end{figure}
%
\todo[inline]{Figures are cited in the text}

@@

\subsection{Control Agent Functionality}
The flow chart of method \texttt{setDeviceStatus} is shown in
Figure~\ref{fig:setDeviceStatus}. The purpose of this method is to set the
status of the desired device. When the method is called, the data dictionary is
obtained which contains the device ID. With this device ID, the API type can be
determined using the SQLite database. Subsequently, the appropriate device API
module can be imported. If the power state exists as a key in the device data
dictionary, the power state of the WeMo Insight Switch will be set as ON or OFF.
If the duty cycle key exists, the duty cycle of the single board computer motor
drivers is set. If the shutdown key is set, the single board computer is
shutdown. In order to reconnect to the single board computer, the board must be
started and receiver program ran. If necessary, the device must be reconnected
to the WiFi network. %
%
\begin{figure}
    \centering
    \includegraphics[scale=0.5]{figs/setDeviceStatus.pdf}
    \caption{setDeviceStatus Flow Chart}
    \label{fig:setDeviceStatus}
\end{figure}
%
\todo[inline]{Figures are not cited in the text}

To obtain necessary data quantities from the device, the
\texttt{getDeviceStatus} method is defined. Once the proper data parameters are
obtained, the \texttt{getState} function defined in the devices API module can
be called with the data parameters \replace{like}{, such as} power state and
status. Once the agent has finished sending these to the device, a request is
sent to the web server to inform the server that it completed searching for the
required device data. %

@@

\subsection{Scheduling Agent Functionality}
The scheduling agent is able to update the device status of each device dependent on whether a schedule is set for the specific time period and day. One of the methods that is called, \texttt{updateScheduleFromServer} is invoked when the user presses the "Update Schedule" button from the UI on the scheduling page. A flow chart of this method is shown in Figure~\ref{fig:updateScheduleFromServer}. When this method is called the desired schedule is loaded in as a dictionary and parsed to extract the necessary periods and given day. First the times are stored in military time in the database for more convenient storage and parsing later on. Then, a table is created in the Apache Cassandra database for the device for the provided data and the device ID is embedded. The table's data is destroyed to ensure there are no errors regarding overlapping schedules. Lastly, all the scheduling periods extracted from the dictionary are stored as rows in the table. 
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/updateScheduleFromServer.pdf}
    \caption{updateScheduleFromServer Flow Chart}
    \label{fig:updateScheduleFromServer}
\end{figure}
A second method that is run inside each device thread is \texttt{periodicDeviceUpdateMethod} which is started when the discovery agent sets the discovered device to active. By first loading the device's API name, the scheduling agent can begin checking for scheduling periods inside an infinite loop. The status dictionary is queried from the Cassandra database and loaded into a dictionary. All these scheduling periods are looped over for the current day while constantly checking whether the current time in seconds is within the starting and ending time. A conversion of both starting and ending time to seconds is necessary as it is challenging to work with these quantities in standard and military time when comparing times. If the current time does lie inside the scheduling period, the device's state is set dependent on the API. 
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/periodicDeviceUpdateMethod.pdf}
    \caption{periodicDeviceUpdateMethod Flow Chart}
    \label{fig:periodicDeviceUpdateMethod}
\end{figure}

\section{Desktop GUI Functionality}
The functionality of the desktop GUI launched when the user runs the Python script titled \texttt{GUI.py} is shown in Figure~\ref{fig:desktopgui}. Packages used to construct the GUI include tkinter which is a Python interface for the Tcl/Tk GUI toolkit. When the GUI is started up, the title, buttons, and labels are created along with ties to the callback functions \texttt{startCallback} and \texttt{stopCallback}. The \texttt{startCallback} function is called when the user presses the "Start iBEMS" button. This function first checks whether iBEMS is already running by checking for processes already running on the machine including the web server itself and the three agents. This is performed using the command \texttt{ps -aux}. After this has been completed, an error popup is shown preventing another instance of the software from running. This prevents errors associated with copies of agents and web servers running simultaneously. To properly stop the software, the "Stop iBEMS" button will shutdown the software by first finding the process ID's associated with the agents and web server. To perform this, it will place the output of \texttt{ps -aux | grep [process]} into a text file where "process" is the name of the target process. A file descriptor of the process status output text file is instantiated and all the lines are read in to be parsed. Each process output is split by spaces and the second element in the list is denoted as the process id. Then, using the \texttt{kill} command, these processes are killed. 
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{figs/GUI_Diagram.pdf}
    \caption{Python desktop GUI Functionality}
    \label{fig:desktopgui}
\end{figure}

@@

The embedded computer needed some software to be able to connect to and communicate with the iBEMS Core. To achieve this, a program consisting of 2 functions for connecting and communicating is used.
\medbreak
The first of these functions is \texttt{connect\_to\_iBEMS}. This function first turns on the red LED on the embedded computer to indicate it is not yet connected. Then it creates a socket using a multicast IP address that the corresponding API in the iBEMS core will be looking for. Once the socket is created, the embedded computer will enter a loop and wait for the iBEMS core to make the initial connection. When that connection is made, it will exit the loop, save the IP address of the iBEMS core, send a confirmation message, then turn on the green LED before closing the multicast socket.
\medbreak
The second function, \texttt{communicate\_with\_iBEMS} will open another socket but with the IP address of the iBEMS core found in \texttt{connect\_to\_iBEMS}. It will then enter a indefinite loop to continually receive data from the iBEMS core. There are 4 different messages that the iBEMS core sends to the embedded computer. First, it will check if the iBEMS core is telling it to shut down with the command "Shutdown." If so, the embedded computer will immediately shut down. Second, if the data sent by iBEMS is "status," the embedded computer will take a reading from the circuit described in Chapter~\ref{ch: Chapter2} section 3. In case the user decides to shut down the iBEMS core without turning off the embedded computer, another message "disconnect" will be sent in which case the embedded computer will exit \texttt{communicate\_with\_iBEMS} and start the entire program over again. Finally, if iBEMS is not sending any of the above options, it means that the user is sending a new duty cycle to drive the motors with. Since iBEMS only sends messages with the string data type, this has to be converted to a float in order to call the motor driver function.

>>>>

% Talk about Zero MQ
All three agents communicate with each other and the web server using the Zero
MQ asynchronous messaging library. Essentially, this library
works as a way to implement inter process communication without a message
broker~\cite{zeromq}. In other words, different processes are able to communicate with each
other without any central bus. This is convenient as fewer processes are needed
for the system to function. Lowering the number of overall processes lowers the
RAM and CPU usage of the software. The library is ported to many different
programming languages; however we are using the Python port titled Pyzmq to
implement in our code base.
%
\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{figs/pubSubAgents.pdf}
    \caption{Publish Subscribe Communication using ZeroMQ}
    \label{fig:pubSubAgents}
\end{figure}

@@

\subsection{Control Agent Functionality}
The flow chart of method \texttt{setDeviceStatus} is shown in
Figure~\ref{fig:setDeviceStatus}. The purpose of this method is to set the
status of the desired device. When the method is called, the data dictionary is
obtained which contains the device ID. With this device ID, the API type can be
determined using the SQLite database. Subsequently, the appropriate device API
module can be imported. If the power state exists as a key in the device data
dictionary, the power state of the WeMo Insight Switch will be set as ON or OFF.
If the duty cycle key exists, the duty cycle of the single board computer motor
drivers is set. If the shutdown key is set, the single board computer is
shutdown. In order to reconnect to the single board computer, the board must be
started and receiver program ran. If necessary, the device must be reconnected
to the WiFi network. %
%
\begin{figure}
    \centering
    \includegraphics[scale=0.5]{figs/setDeviceStatus.pdf}
    \caption{setDeviceStatus Flow Chart}
    \label{fig:setDeviceStatus}
\end{figure}

To obtain necessary data quantities from the device, the
\texttt{getDeviceStatus} method, defined in Figure~\ref{fig:getDeviceStatus}, is called. Once the proper data parameters are
obtained, the \texttt{getState} function defined in the devices API module can
be called with the data parameters such as power state and
status. Once the agent has finished sending these to the device, a request is
sent to the web server to inform the server that it completed searching for the
required device data. %

@@

\subsection{Scheduling Agent Functionality}
The scheduling agent is able to update the device status of each device dependent on whether a schedule is set for the specific time period and day. One of the methods that is called, \texttt{updateScheduleFromServer} is invoked when the user presses the \say{Update Schedule} button from the UI on the scheduling page. A flow chart of this method is shown in Figure~\ref{fig:updateScheduleFromServer}. When this method is called the desired schedule is loaded in as a dictionary and parsed to extract the necessary periods and given day. First the times are stored in military time in the database for more convenient storage and parsing later on. Then, a table is created in the Apache Cassandra database for the device for the provided data and the device ID is embedded. The table's data is destroyed to ensure there are no errors regarding overlapping schedules. Lastly, all the scheduling periods extracted from the dictionary are stored as rows in the table. 
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/updateScheduleFromServer.pdf}
    \caption{updateScheduleFromServer Flow Chart}
    \label{fig:updateScheduleFromServer}
\end{figure}
A second method that is run inside each device thread is \texttt{periodicDeviceUpdateMethod}, defined in Figure~\ref{fig:periodicDeviceUpdateMethod}, is started when the discovery agent sets the discovered device to active. By first loading the device's API name, the scheduling agent can begin checking for scheduling periods inside an infinite loop. The status dictionary is queried from the Cassandra database and loaded into a dictionary. All these scheduling periods are looped over for the current day while constantly checking whether the current time in seconds is within the starting and ending time. A conversion of both starting and ending time to seconds is necessary as it is challenging to work with these quantities in standard and military time when comparing times. If the current time does lie inside the scheduling period, the device's state is set dependent on the API. 
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.5]{figs/periodicDeviceUpdateMethod.pdf}
    \caption{periodicDeviceUpdateMethod Flow Chart}
    \label{fig:periodicDeviceUpdateMethod}
\end{figure}

\section{Desktop GUI Functionality}
The functionality of the desktop GUI launched when the user runs the Python script titled \texttt{GUI.py} is shown in Figure~\ref{fig:desktopgui}. Packages used to construct the GUI include tkinter which is a Python interface for the Tcl/Tk GUI toolkit. When the GUI is started up, the title, buttons, and labels are created along with ties to the callback functions \texttt{startCallback} and \texttt{stopCallback}. The \texttt{startCallback} function is called when the user presses the \say{Start iBEMS} button. This function first checks whether iBEMS is already running by checking for processes already running on the machine including the web server itself and the three agents. This is performed using the command \texttt{ps -aux}. After this has been completed, an error popup is shown preventing another instance of the software from running. This prevents errors associated with copies of agents and web servers running simultaneously. To properly stop the software, the \say{Stop iBEMS} button will shutdown the software by first finding the process ID's associated with the agents and web server. To perform this, it will place the output of \texttt{ps -aux | grep [process]} into a text file where \say{process} is the name of the target process. A file descriptor of the process status output text file is instantiated and all the lines are read in to be parsed. Each process output is split by spaces and the second element in the list is denoted as the process id. Then, using the \texttt{kill} command, these processes are killed. 
\begin{figure}[H]
    \centering
    \includegraphics[scale=0.6]{figs/GUI_Diagram.pdf}
    \caption{Python desktop GUI Functionality}
    \label{fig:desktopgui}
\end{figure}

@@

The embedded computer needed some software to be able to connect to and communicate with the iBEMS Core. To achieve this, a program consisting of 2 functions for connecting and communicating is used.
\medbreak
The first of these functions is \texttt{connect\_to\_iBEMS}. This function first turns on the red LED on the embedded computer to indicate it is not yet connected. Then it creates a socket using a multicast IP address that the corresponding API in the iBEMS core will be looking for. Once the socket is created, the embedded computer will enter a loop and wait for the iBEMS core to make the initial connection. When that connection is made, it will exit the loop, save the IP address of the iBEMS core, send a confirmation message, then turn on the green LED before closing the multicast socket.
\medbreak
The second function, \texttt{communicate\_with\_iBEMS} will open another socket but with the IP address of the iBEMS core found in \texttt{connect\_to\_iBEMS}. It will then enter a indefinite loop to continually receive data from the iBEMS core. There are 4 different messages that the iBEMS core sends to the embedded computer. First, it will check if the iBEMS core is telling it to shut down with the command \say{Shutdown}. If so, the embedded computer will immediately shut down. Second, if the data sent by iBEMS is \say{status}, the embedded computer will take a reading from the circuit described in Chapter~\ref{ch: Chapter2} section 3. In case the user decides to shut down the iBEMS core without turning off the embedded computer, another message \say{disconnect} will be sent in which case the embedded computer will exit \texttt{communicate\_with\_iBEMS} and start the entire program over again. Finally, if iBEMS is not sending any of the above options, it means that the user is sending a new duty cycle to drive the motors with. Since iBEMS only sends messages with the string data type, this has to be converted to a float in order to call the motor driver function.

### 2021-05-04 parts/40-ExperimentalResults.tex
Initial feedback by Dr. Miah
Updated report

\noindent
Here, the user will simply click the "Start iBEMS" button to launch the web server and agents. When the user is finished, all agents and the web server can be shut down by clicking "Stop iBEMS." In case the user accidentally clicks the "Start iBEMS" button while iBEMS is already running, then the following error message will appear:

@@

Figure~\ref{fig:active_devices} shows the active devices page (mode 3) which is loaded upon clicking "Active Devices" in the navigation bar. Here, all the connected devices are shown in order of when they connected to iBEMS. As mentioned previously, control of the WeMo Insight Switch is limited to turning it on and off while the embedded computer's motor speed can be controlled by submitting different duty cycles. Additionally, the embedded computer can be completely turned off by clicking the "Shutdown" button. Both supported devices also log their power usage at regular intervals. A plot of these power usage data points can be viewed by clicking "View Status Plots."

@@

After clicking "View Status Plots," a modal will pop up for the user to further interact with. By default, power usage data points for the current day are loaded at first, but another day can be selected by clicking on the calendar icon in the lower right corner. The plot is then updated by clicking "Update Plots." This is done by collecting data from the Apache Cassandra database and simply plotting all the points found for the specified day. Underneath the plot, the total energy consumed for the specified day is displayed. That total energy is found using the trapezoid method for integration on the plot.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.35]{figs/Applications_screen.png}
    \caption{Scheduling Page}
    \label{fig:schedulingl}
\end{figure}

Mode 4, or the scheduling page, can be loaded by clicking the "Device Scheduling" button in the navigation bar. Much like the active devices page, each connected device is listed in order of when they connected to iBEMS. Instead of directly controlling the devices, the user can enter in time periods when they want each device to maintain a specified status. For example, the WeMo Insight Switch can be scheduled to be on from 5 to 8 P.M. on Fridays. Likewise, the embedded computer can be scheduled to maintain a duty cycle of 0.5 for the same time period every Friday. Scheduled times can be added with the "Add new Period" and deleted by clicking the red "X" by the corresponding time period.

>>>>

\noindent
Here, the user will simply click the \say{Start iBEMS} button to launch the web
server and agents. When the user is finished, all agents and the web server can
be shut down by clicking \say{Stop iBEMS}. In case the user accidentally clicks the
\say{Start iBEMS} button while iBEMS is already running, then the following error
message will appear:

@@

Figure~\ref{fig:active_devices} shows the active devices page (mode 3) which is loaded upon clicking \say{Active Devices} in the navigation bar. Here, all the connected devices are shown in order of when they connected to iBEMS. As mentioned previously, control of the WeMo Insight Switch is limited to turning it on and off while the embedded computer's motor speed can be controlled by submitting different duty cycles. Additionally, the embedded computer can be completely turned off by clicking the \say{Shutdown} button. Both supported devices also log their power usage at regular intervals. A plot of these power usage data points can be viewed by clicking \say{View Status Plots}.

@@

After clicking \say{View Status Plots}, a modal will pop up for the user to further
interact with. By default, power usage data points for the current day are
loaded at first, but another day can be selected by clicking on the calendar
icon in the lower right corner. The plot is then updated by clicking \say{Update
Plots}. This is done by collecting data from the Apache Cassandra database and
simply plotting all the points found for the specified day. Underneath the plot,
the total energy consumed for the specified day is displayed. That total energy
is found using the trapezoid method for integration on the plot. %
%
\begin{figure}
    \centering
    \includegraphics[scale=0.35]{figs/Applications_screen.png}
    \caption{Scheduling Page}
    \label{fig:schedulingl}
\end{figure}
%

Mode 4, or the scheduling page, can be loaded by clicking the \say{Device
Scheduling} button in the navigation bar. Much like the active devices page,
each connected device is listed in order of when they connected to iBEMS.
Instead of directly controlling the devices, the user can enter in time periods
when they want each device to maintain a specified status. For example, the WeMo
Insight Switch can be scheduled to be on from 5 to 8 P.M. on Fridays. Likewise,
the embedded computer can be scheduled to maintaian a duty cycle of 0.5 for the
same time period every Friday. Scheduled times can be added with the \say{Add new
Period} and deleted by clicking the red \say{X} by the corresponding time period.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../finalReport"
%%% End:
